\Large \bf Cyclone: Replication Middleware for NVM Applications

### 2016-09-27 paper/paper.tex
Fixing captions.

\end{verbatim}
  }
\caption{A Persistent Linked List}
\label{fig:example}
\end{figure}

@@

Although the common case path in RAFT is straightforward, it still requires
hundreds of cycles (or a few microseconds) to process each log entry, which is a
significant amount in the face of sub 10 us network latency between nodes with
DPDK. We amortize this overhead when operating under load by batching multiple
RPC calls together and treating the batch as a single RAFT log entry.  DPDK by
itself can efficiently batch incoming packets under load, therefore allowing the
user to easily receive a burst of packets (currently limited to 32) rather than
a single packet for a polling call.  DPDK further allows chaining packet buffers
together and treating the chain as a single packet. We chain these packet
buffers together to form a single packet. Since the entire chain is sent as a
single packet when being replicated, the length of a chain is limited by the
size of the coalesced packet, that must fit into an ethernet jumbo frame of
approximately 9KB.

\begin{figure}
\includegraphics[width=0.7\textwidth,height=6cm]{figures/chain.pdf}
\caption{Zero Copy Batching}
\label{fig:zc_batch}
\end{figure}

This set of transformations to incoming request packets from clients at the
leader replica is summarized in Figure~\ref{fig:zc_batch}.

@@

release:
 set client identifier to 3
 for each machine
   Update object
   If machine reponds RPC sequence too old
     Transaction completed by someone else
\end{verbatim}
}
\caption{Distributed Transactions}
\label{fig:dist_tx}
\end{figure}

@@

\begin{figure}
\begin{tabular}{cc}
\begin{minipage}{0.25\textwidth}
  \hspace{-0.17in}
  \includegraphics[width=\textwidth,height=3cm]{results/replication_mops_0.pdf}
\end{minipage}&
\begin{minipage}{0.25\textwidth}
  \hspace{-0.37in}
  \includegraphics[width=\textwidth,height=3cm]{results/replication_gbps_0.pdf}
\end{minipage}\\
\begin{minipage}{0.25\textwidth}
  \hspace{-0.17in}
  \includegraphics[width=\textwidth,height=3cm]{results/replication_mops_512.pdf}
\end{minipage}&
\begin{minipage}{0.25\textwidth}
  \hspace{-0.37in}
  \includegraphics[width=\textwidth,height=3cm]{results/replication_gbps_512.pdf}
\end{minipage}
\end{tabular}
\caption{Pure Replication}
\label{fig:pure_rep}
\end{figure}

@@

\begin{figure}
\begin{tabular}{cc}
\begin{minipage}{0.25\textwidth}
  \hspace{-0.17in}
  \includegraphics[width=\textwidth,height=3cm]{results/cc_mops.pdf}
  \caption{Crash Consistency}
  \label{fig:cc_rep}
\end{minipage} &
  \hspace{-0.37in}
\begin{minipage}{0.25\textwidth}
  \includegraphics[width=\textwidth,height=3cm]{results/app_mops.pdf}
  \caption{Hash Table}
  \label{fig:app_rep}
\end{minipage}
\end{tabular}
\end{figure}

>>>>

\end{verbatim}
  }
\vspace{-0.2in}
\caption{A Persistent Linked List}
\label{fig:example}
\end{figure}

@@

Although the common case path in RAFT is straightforward, it still requires
hundreds of cycles (or a few microseconds) to process each log entry, which is a
significant amount in the face of sub 10 us network latency between nodes with
DPDK. We amortize this overhead when operating under load by batching multiple
RPC calls together and treating the batch as a single RAFT log entry.  DPDK by
itself can efficiently batch incoming packets under load, therefore allowing the
user to easily receive a burst of packets (currently limited to 32) rather than
a single packet for a polling call.  DPDK further allows chaining packet buffers
together and treating the chain as a single packet. We chain these packet
buffers together to form a single packet. Since the entire chain is sent as a
single packet when being replicated, the length of a chain is limited by the
size of the coalesced packet, that must fit into an ethernet jumbo frame of
approximately 9KB. Figure~\ref{fig:zc_batch} summarizes this set of
transformations to incoming request packets from clients at the leader replica.

\begin{figure}
\includegraphics[width=0.9\columnwidth]{figures/chain}
\vspace{-0.15in}
\caption{Zero Copy Batching}
\label{fig:zc_batch}
\end{figure}

@@

release:
 set client identifier to 3
 for each machine
   Update object
   If machine reponds RPC sequence too old
     Transaction completed by someone else
\end{verbatim}
}
\vspace{-0.22in}
\caption{Distributed Transactions}
\label{fig:dist_tx}
\end{figure}

@@

\begin{figure}
\begin{tabular}{cc}
\begin{minipage}{0.25\textwidth}
  \hspace{-0.17in}
  \includegraphics[width=\textwidth,height=3cm]{results/replication_mops_0.pdf}
\end{minipage}&
\begin{minipage}{0.25\textwidth}
  \hspace{-0.37in}
  \includegraphics[width=\textwidth,height=3cm]{results/replication_gbps_0.pdf}
\end{minipage}\\
\begin{minipage}{0.25\textwidth}
  \hspace{-0.17in}
  \includegraphics[width=\textwidth,height=3cm]{results/replication_mops_512.pdf}
\end{minipage}&
\begin{minipage}{0.25\textwidth}
  \hspace{-0.37in}
  \includegraphics[width=\textwidth,height=3cm]{results/replication_gbps_512.pdf}
\end{minipage}
\end{tabular}
\caption{Evaluation of pure replication performance}
\label{fig:pure_rep}
\end{figure}

\begin{figure}[htb]
%\vspace{-0.2in}
\centering
\begin{tabular}{c}
\includegraphics[height=3cm,width=0.8\columnwidth]{results/cc_mops.pdf}
\end{tabular}
\vspace{-0.22in}
\caption{Evaluation of replication performance with crash consistency}
\label{fig:cc_rep}
\vspace{-0.08in}
\end{figure}

\begin{figure}[htb]
%\vspace{-0.2in}
\centering
\begin{tabular}{c}
\includegraphics[height=3cm,width=0.8\columnwidth]{results/app_mops.pdf}
\end{tabular}
\vspace{-0.22in}
\caption{Evaluation of in-memory hash table performance with 3-way crash consistent replication}
\label{fig:app_rep}
\vspace{-0.08in}
\end{figure}

@@
